Dynamics of the Lower Solar Atmosphere

### 2024-07-22 introduction/intro.tex
Updates from Overleaf

The Sun is our nearest astrophysical object, which serves as a natural laboratory for various branches of Physics - atomic physics, spectroscopy, turbulence, magnetohydrodynamics, stellar evolution, dynamo and magnetism and plays a key role in space and terrestrial weather. The Sun is also the primary source of light and energy on earth. So it is only natural that we try to understand the different physical processes involved in the energectics of the Sun, which indirecrtly affects life on Earth. In this chapter I briefly introudce the Sun and various layers of its atmosphere. At the end we provide a motivation for the thesis.

The Sun is a G2V star, with surface luminosity $3.86~\times~10^{26}$ W and an effective temperature of $\sim 5780~K$. The Sun is mostky made out of Hydrogen(92.1\%) and Helium(7.8\%) along with negligible quantities of heavier elements C, N, O, Mg, Si, Ne and Fe. The study of the Sun can be mainly divided into three components: the Solar interior, the Solar atmosphere and the Heliosphere.

@@

%% ############# %%
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{Figures/solar_atm.png}
    \caption{The variation of electron temperature (solid line) and electron density ($\mamthrm{N_{e}}$, dashed line) and density of neutral hydrogen atoms ($\mathrm{N_{H}}$, dotted- dashed line) in the solar atmosphere as derived based on the 1-D model calcula- tions by \sr{Ref. here}.}
    \label{fig_solar_atm}
\end{figure}
%% ############# %%

@@

%%%%%%%%%%%%%%%%
\begin{figure}[ht!]
    \centering
    \includegraphics[trim={1cm 3cm 2cm 5cm},clip,width=0.8\textwidth]{Figures/sji_images.pdf}
    \caption{IRIS SJI Slit-jaw images of NOAA AR 13521 on Dec 21st, 2023 in \ion{Mg}{2} 2796~\AA~(left panel) showing the upper Chromosphere. The right panel shows the same active region in 2832~\AA~continuum corresponding to upper photosphere.}
    \label{fig:sji_features}
\end{figure}
%%%%%%%%%%%%%%%%

In fig.~\ref{fig:sji_features} we show the NOAA AR 13521 in IRIS SJI 2796~\AA (left panel) and 2832~\AA (right panel). The dark sunspots and plage regions surrounding it are clearly visible in the 2832~\AA wavelength window. In the 2796~\AA window we see the plage along with light bridges more clearly.

@@

The transition region above the Chromosphere is a thin, dynamic layer where we witness a dramatic increase in temperature by two orders of magnitude along with a similar decrease in electron density by nearly 5-6 orders of magnitude which is demonstrated in fig. \ref{fig_solar_atm}. In general the this layer is roughly $\sim$ 100 km in thickness, but that can change depending on various dynamic conditions of Chromosphere($\sim~10^{4}~K$) below, or Corona($\sim~10^{6}~K$) on top. The transition region is generally characterized by the steep change in the temperature, pressure gradients, drastic change in local optical depth and competition between gas pressure and magnetic pressure. The transition region also manifests the ARs as various magnetic features such as small scale brightenings, jets, spicules, fibrils etc.

@@

The outermost layer of the Solar atmosphere is the Corona. The Corona is only visible in naked eyes during the total solar eclipse or via Coronagraphs. It maintains a steady temperature of 1-2 Mk during ambient conditions, but can rise upto tens of MK during solar flares. The coronal continuum spectrum is produced due to Thompson scattering of photons from photosphere off coronal electrons. Corona also emits in various emission lines, e.g. Mg, Fe, Si, S, Ca, O etc. across a wide band of elctro magnetic spectrum ranging from X-ray to visible wavelengths.

@@

In September 1, 1859, R.C. Carrington and R. Hodgson observed the first flare in the continuum of white light\citep{carrington1859,hodgson1859}. The localized brightenings on the Sun have remained an enigma ever since. We have been observing the local flaring events acrsoss all wavelenths from both ground and space based observatories.  Shortly after the observation by Carrington and Hodgson, people started studying the Sun extensively in the H$\alpha$ line which is formed in the Chromosphere, and the reports of flaring events became more and more frequent and progressivly more and more complex. No two events were similar, as there were variations observed in source of size, ejections of plasma along with shockwaves driving into the interplanetary space. Advances of radio technology during the second world war ensured detections of prescence of non-thermal electrons in the solar corona, during military radar operations \citep{hey46}. Around the same time S.E. Forbrush noticed ground level cosmic ray enhancement during major solar flares. These discoveries illuded that the flaring events do not only involve the thermal plasma, but is somehow connects with high energy particles and involves the corona. in the 1950s we started observing the Sun in hard X-rays ($\ge~10~keV$) with rockets and baloons. \cite{peterson59} discovered the first hard X-ray emission during a flare in 1958. Later on, it was deduced from the observations of the enhancements observed in radio and hard X-rays that, the the ejected energetic particles may contain a substantial fraction of the intial energy released \citep{brown71}. The hard X-ray is created by the bremsstrahlung of the electrons colliding into dense material, resulting in a power-law energy distribution. The braodband radio emission from 1 to 100 GHz is created from gyrosynchrotron emission. Finally, observations in EUV and soft X-ray($\le$~10~keV) have shown that the energy released form the flare heats the plasma contained in the coronal loops to temperatures beyond 30 MK.

@@

\cite{neupert68} observed a curious corelation that, the soft X-ray flux during the rise phase of the flare is proportional to the time integral of the centimeter radio flux since the start of the flare. The centimeter radio flux is emitted by relativistic electrons. So, later on the same corelation was found between the hard X-ray flux and soft X-ray flux and can be expressed as,

@@

This emperical relation is known as the ``Neupert effect''. \cite{neupert68} had already suggested that thismay be due to a causal relationship between the thermal plasma and the energetic electrons. The logical explanation is: the soft X-ray mainly originates from a thermal plasma heated by the energy of the flaring event deposited by the flare acclerated electrons. It is important to mention that we know now, eqn.\ref{npt_eff_eq} is only valid if cooling by conduction of radiation is negligible.

%% ################################################################# %%
\subsection{Standard model of solar flare}\label{sol_flr_std_mod}
%% ################################################################# %%

@@

%%%%%%%%%%%%%%%%%
\begin{enumerate}
    \item The magnetic reconnetion happens in corona, releasing the magnetic free energy. Electrons and energetic particles from the reconnetion site are acclerated along the realigned magnetic field lines. The acclerated particles that escape along the open field lines towards the earth gives rise to the particle events seen from earth.
    \item The acclerated particles move along the field lines downwards along the magnetic field lines, giving rise to the microwave observations seen from falres via gyromagnetic radiation.
    \item The acclerated particles hit the Chromosphere which is considerably denser than the Corona, giving rise to Hard X-ray and gamma ray observed from the footpoints. This also explains why the coronal hard X-ray source is considerably softer than the footpoints. The energetic particles deposit their energy into the local Chromosphere, as they go through series of collision and eventually thermalize.
    \item  As the plasma thermalizes, it starts emitting in thermal bremsstrahlung giving rise to the soft X-ray observed. Also, as the energy is deposited into the Chromosphere from the acclerated particles, it heats the local Chromosphere environment it gradually increases the local pressure. 
    \item As the pressure grows, when the pressure gradient builds up enough the local plasma starts expanding upwards(essentially due to buoyancy) and slowly fills up the coronal loops with soft X-ray emitting plasma. This phenomenon is known as "Chromospheric evaporation". This was dorectly observed later on, in blue-shifted lines of hot material.
    \item This whole scenario explains the Neupert effect. As the energy form the acclerated particles is converted into the soft X-ray emitting plasma, and it builds up over time. That explains the soft X-ray being proportional to the time integral of the hard X-ray flux.
\end{enumerate}
%%%%%%%%%%%%%%%%%

This whole scenario is known as the ``Standard model of solar flare''. While the standard model is an attempt to explain and unify various kind of differences seen from the neumerous flares we observe, there are several cases where the stnadard model cannot explain the observations. For example, there have been observations of falres where the hard X-ray footpoint do not form. It is proposed that in these cases the plasma in the coronal loops is so dense that the acclerated particle collide enough to thermalize within the flare loops before reaching the Chromosphere, deffusing the energy more evenly within the loop, rather than dumping it at the base of the loops \citep{veronig02,veronig04}. Another flare which previously occured at the same region might explain the denser coronal loops \citep{strong84,bone07}.

@@

With an experience of observing solar flares for more than 150 years, remarkably enough, we have barely started scratching the surface of the complexity involved with the solar flares. The reconfiguring of magnetic structure, which almost always involves complex geometry, making almost all events unique in some sense. After that the released magnetic free energy is transported accross various layers of the sun and converted into various other forms of energy. Consodering how the energy is transformed the magnetic energy of the active region that is released after the reconnection into the reconnection outflow jets, the kinetic energy of escaping particles, the thermal and the kinetic energy of the Chromospheric plasma evaporating, the radiative and conductive losses. In case of the eruptive events, there is the added complexity of the kinetic and potential energy of the CMEs, the enrgy of the shcoks and the kinetic energy of the solar energetic particles.

Inorder to constrain the models of solar eruptions and various nuanced aspects of it, like magnetic reconnection, particle accleration, heating etc. detailed quantitative characterization is absolutely necessary. There have been several studies that have tried to quantify the partition between various subsets of the energies. The questions that are perticularly important are:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
    \item \textbf{If an active region can have enough free enrgy to account for the total energy relased in the solar flares and/or CMEs.}
    \item \textbf{What is the energy partition betwen flares and CMEs.}
    \item \textbf{If the non-thermal component have enough energy to power up the thermal component.}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

It is generally well known by now that the active region have enough magnetic free energy to power the flare and CME \citep{emslie12,ash17}. The partition of energy between the flare and associated CME is much more fuzzy. \cite{emslie12} found that the flare and CME have energies of same order of magnitude, while \cite{ash17} concluded the flare dominates the CME in-terms of the energy. However the simple question, whether the non-thermal component of the flares have enough enrgy is still not resolved as even the most recent studies contradict each other in the most puzzling fashion. \cite{warmuth20} discussed the contradictions arising from some of the studies\citep{stosire07,emslie12,inglis14,warmuth16a,warmuth16b,ash17}. The details of the studies can be summarized as follows:

@@

The bolometric energy serves as a representation of the overall energy released during solar flares. Regardless of how energy is released in a solar flare, whether through direct plasma heating, rapid bulk flows, or nonthermal particle processes—the ultimate outcome is thermalization and subsequent radiation across the electromagnetic spectrum. Given that bolometric energy encompasses the entire spectrum, it is anticipated to reflect the total energy originally released. It's important to note that this specifically pertains to the energy liberated within the flare and does not encompass the energy associated with a concurrent coronal mass ejection (CME) or filament eruption. So, \cite{warmuth20} used the bolometric energy released in solar flares, to compare various studies on equal footing. Here we will discuss some of the main issues \cite{warmuth20} identifies comparing these studies.

@@

A possible reason can be attributed to different thermal models used to model the thermal component of the flares. {\it RHESSI} usually yields a higher temperature and lower emission measure compared to {\it GOES} due to the highly multi thermal nature of the flaring plasma \citep{bataglia05,ryan14,warmuth16a}. Although the {\it GOES} temperature is higher by a factor of 1.4, it is not dependant on the flare class. Along with that, \cite{warmuth20} also investigated whether assuming a isothermal or multithermal model introduces any differences in the thermal energy estimates. They reported no significant differences due to differences of models (refer to Fig. 2 and the corresponding discussion in \cite{warmuth20}).

@@

%%%%%%%%%
\begin{itemize}
    \item The primary challenge in estimating the thermal energy of the hot plasma stems from determining the distribution of the Differential Emission Measure (DEM), and the radiating plasma volume.
    \item The dissipation of energy from the hot plasma is substantial. Although there is widespread agreement regarding radiative losses across studies, the extent of conductive losses disagree significantly between the studies.
    \item The non-thermal energy in injected electrons is strongly dependent on the poorly constrained low-energy cutoff.
    \item The thermal and non-thermal energy partition changes with flare class. In smaller flares, there appears to be a deficiency of energetic electrons, whereas in larger flares, the injected non-thermal energy seems to sufficient in powering the thermal component. Does this signify the existance of an additional third heating source?
\end{itemize}
%%%%%%%%%

@@

This illustrates the necessity of more observatories operating at the transition region wavelengths for more comprehensive understanding about how the solar flares manifest and affect the dynamics and heating of the lower solar atmosphere. In this regard, {\suit} onboard Aditya-L1 will play a crucial role in probing the lower solar atmosphere. The various imaging channels of {\suit} would observe the manifestation of flares in transition region at various heights (NB3 $\implies$ \ion{Mg}{2} k 279.6 nm, NB4 $\implies$ \ion{Mg}{2} h 280.3 nm, NB8 $\implies$ \ion{Ca}{2} h 396.8 nm), further lower in the transition region (NB2 $\implies$ blue wing of Mg window, NB5 $\implies$ red wing of Mg window) and Sunspots and possible signature of umbral brightening due to flares at the Photosphere (NB6 300 nm and NB7 388 nm) in full disk. This would also allow us to probe the interaction of the flaring region, with other active regions on disk, giving us a comprehensive overview of the effect of solar flares and their manifestation in the lower solat atmosphere.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
    \item In chapter \ref{c:chap2}, we review various space based missions available and used in this thesis. We also discuss various analysis techniques used in this thesis. We also motivate the importance of {\suit} and its main science goals. We also briefly discuss the specific questions regarding solar flares we can address with {\suit}.
    \item In chapter \ref{c:chap3}, we discussed some of the initial preparatory analysis we did for {\suit}, including the throughput model for {\suit}, how the filters mounted on {\suit} were chosen, the analysis of spacecraft jitter simulation and what effect it would have on the imaging.
    \item In chapter \ref{c:chap4}, we discuss the forward modelling pipeline developed for {\suit}. We use MPS-Atlas simulation and {\it IRIS} observations, with measured transmission profiles of various optical components and the PSF to forward model {\suit} observations. We also discuss a preliminary version of the deconvolution algorithm that will be deployed in the data reduction pipeline.
    \item In chapter \ref{c:chap5}, we describe the stellar calibration scheme and the selection criteria for the standard star target. We also use a sun as a star spectra to evaluate the calibration scheme.
    \item In chapter \ref{c:chap6}, we use existing {\it IRIS} observations of three solar flares to probe how the lower solar atmosphere is affected by the flares. The ratio of the \ion{Mg}{2} k and h lines, is a proxy for the optical depth of the surrounding plasma. Hence, we use the observations of \ion{Mg}{2} lines along HMI magentic field measurements to investigate the effects of magnetic field, if any. \cite{kerr15} conducted a similar study and found signatures of localised heating in the line intensity ratio. We found, that the line intensity ratio shows a correlated increase and decrease with the flare light curve. We argue this to be signature of plasma flow associated with flare, and a change in density of the local environment. This acts as a prelude of what is achievable with {\suit}. We can use a similar method to give full disk context of optical depth, with respect to eruptive events.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\justifying

The Sun is our nearest astrophysical object, which serves as a natural laboratory for various branches of Physics - atomic physics, spectroscopy, turbulence, magneto-hydrodynamics, stellar evolution, dynamo and magnetism and plays a key role in space and terrestrial weather. The Sun is also the primary source of light and energy on earth. So it is only natural that we try to understand the different physical processes involved in the energectics of the Sun, which indirectly affects life on Earth. In this chapter I briefly introduce the Sun and various layers of its atmosphere. At the end we provide a motivation for the thesis.

The Sun is a G2V star, with surface luminosity $3.86~\times~10^{26}$ W and an effective temperature of $\sim 5780~K$. The Sun is mostly made out of Hydrogen(92.1\%) and Helium(7.8\%) along with negligible quantities of heavier elements C, N, O, Mg, Si, Ne and Fe. The study of the Sun can be mainly divided into three components: the Solar interior, the Solar atmosphere and the Heliosphere.

@@

%% ############# %%
\begin{figure}[h!]
    \centering
    \includegraphics[width = 0.8\linewidth]{Figures/solar_atm.png}
    \caption{The variation of electron temperature (solid line) and electron density ($\mamthrm{N_{e}}$, dashed line) and density of neutral hydrogen atoms ($\mathrm{N_{H}}$, dotted- dashed line) in the solar atmosphere as derived based on the 1-D model calculations by \sr{Ref. here}.}
    \label{fig_solar_atm}
\end{figure}
%% ############# %%

@@

%%%%%%%%%%%%%%%%
\begin{figure}[ht!]
    \centering
    \includegraphics[trim={1cm 3cm 2cm 5cm},clip,width=0.8\textwidth]{Figures/sji_images.pdf}
    \caption{IRIS SJI Slit-jaw images of NOAA AR 13521 on Dec 21st, 2023 in \ion{Mg}{2} 2796 {\AA}~(left panel) showing the upper Chromosphere. The right panel shows the same active region in 2832 {\AA}~continuum corresponding to upper photosphere.}
    \label{fig:sji_features}
\end{figure}
%%%%%%%%%%%%%%%%

In fig.~\ref{fig:sji_features} we show the NOAA AR 13521 in IRIS SJI 2796 {\AA} (left panel) and 2832 {\AA} (right panel). The dark sunspots and plage regions surrounding it are clearly visible in the 2832 {\AA} wavelength window. In the 2796 {\AA} window we see the plage along with light bridges more clearly.

@@

The transition region above the Chromosphere is a thin, dynamic layer where we witness a dramatic increase in temperature by two orders of magnitude along with a similar decrease in electron density by nearly 5-6 orders of magnitude which is demonstrated in fig. \ref{fig_solar_atm}. In general the this layer is roughly $\sim$ 100 km in thickness, but that can change depending on various dynamic conditions of Chromosphere($\sim~10^{4}~K$) below, or Corona($\sim~10^{6}~K$) on top. The transition region is generally characterized by the steep change in the temperature, pressure gradients, drastic change in local optical depth and competition between gas pressure and magnetic pressure. The transition region also manifests the ARs as various magnetic features such as small scale brightening, jets, spicules, fibrils etc.

@@

The outermost layer of the Solar atmosphere is the Corona. The Corona is only visible in naked eyes during the total solar eclipse or via Coronagraphs. It maintains a steady temperature of 1-2 Mk during ambient conditions, but can rise upto tens of MK during solar flares. The coronal continuum spectrum is produced due to Thompson scattering of photons from photosphere off coronal electrons. Corona also emits in various emission lines, e.g. Mg, Fe, Si, S, Ca, O etc. across a wide band of electromagnetic spectrum ranging from X-ray to visible wavelengths.

@@

In September 1, 1859, R.C. Carrington and R. Hodgson observed the first flare in the continuum of white light\citep{carrington1859,hodgson1859}. The localized brightening on the Sun have remained an enigma ever since. We have been observing the local flaring events across all wavelengths from both ground and space based observatories.  Shortly after the observation by Carrington and Hodgson, people started studying the Sun extensively in the H$\alpha$ line which is formed in the Chromosphere, and the reports of flaring events became more and more frequent and progressively more and more complex. No two events were similar, as there were variations observed in source of size, ejections of plasma along with shock waves driving into the interplanetary space. Advances of radio technology during the second world war ensured detection of presence of non-thermal electrons in the solar corona, during military radar operations \citep{hey46}. Around the same time S.E. Forbrush noticed ground level cosmic ray enhancement during major solar flares. These discoveries eluded that the flaring events do not only involve the thermal plasma, but is somehow connects with high energy particles and involves the corona. in the 1950s we started observing the Sun in hard X-rays ($\ge~10~keV$) with rockets and balloons. \cite{peterson59} discovered the first hard X-ray emission during a flare in 1958. Later on, it was deduced from the observations of the enhancements observed in radio and hard X-rays that, the the ejected energetic particles may contain a substantial fraction of the initial energy released \citep{brown71}. The hard X-ray is created by the bremsstrahlung of the electrons colliding into dense material, resulting in a power-law energy distribution. The broadband radio emission from 1 to 100 GHz is created from gyrosynchrotron emission. Finally, observations in EUV and soft X-ray($\le$~10~keV) have shown that the energy released form the flare heats the plasma contained in the coronal loops to temperatures beyond 30 MK.

@@

\cite{neupert68} observed a curious correlation that, the soft X-ray flux during the rise phase of the flare is proportional to the time integral of the centimeter radio flux since the start of the flare. The centimeter radio flux is emitted by relativistic electrons. So, later on the same correlation was found between the hard X-ray flux and soft X-ray flux and can be expressed as,

@@

This empirical relation is known as the ``Neupert effect''. \cite{neupert68} had already suggested that this may be due to a causal relationship between the thermal plasma and the energetic electrons. The logical explanation is: the soft X-ray mainly originates from a thermal plasma heated by the energy of the flaring event deposited by the flare accelerated electrons. It is important to mention that we know now, Eqn.\ref{npt_eff_eq} is only valid if cooling by conduction of radiation is negligible.

%% ################################################################# %%
\subsection{``Standard'' model of solar flare}\label{sol_flr_std_mod}
%% ################################################################# %%

@@

%%%%%%%%%%%%%%%%%
\begin{enumerate}
    \item The magnetic reconnetion happens in corona, releasing the magnetic free energy. Electrons and energetic particles from the reconnetion site are accelerated along the realigned magnetic field lines. The accelerated particles that escape along the open field lines towards the earth gives rise to the particle events seen from earth.
    \item The accelerated particles move along the field lines downwards along the magnetic field lines, giving rise to the microwave observations seen from flares via gyro magnetic radiation.
    \item The accelerated particles hit the Chromosphere which is considerably denser than the Corona, giving rise to Hard X-ray and gamma ray observed from the foot points. This also explains why the coronal hard X-ray source is considerably softer than the foot points. The energetic particles deposit their energy into the local Chromosphere, as they go through series of collision and eventually thermalize.
    \item  As the plasma thermalizes, it starts emitting in thermal bremsstrahlung giving rise to the soft X-ray observed. Also, as the energy is deposited into the Chromosphere from the accelerated particles, it heats the local Chromosphere environment it gradually increases the local pressure. 
    \item As the pressure grows, when the pressure gradient builds up enough the local plasma starts expanding upwards(essentially due to buoyancy) and slowly fills up the coronal loops with soft X-ray emitting plasma. This phenomenon is known as "Chromospheric evaporation". This was directly observed later on, in blue-shifted lines of hot material.
    \item This whole scenario explains the Neupert effect. As the energy form the accelerated particles is converted into the soft X-ray emitting plasma, and it builds up over time. That explains the soft X-ray being proportional to the time integral of the hard X-ray flux.
\end{enumerate}
%%%%%%%%%%%%%%%%%

This whole scenario is known as the ``Standard'' model of solar flare. While the standard model is an attempt to explain and unify various kind of differences seen from the numerous flares we observe, there are several cases where the standard model cannot explain the observations. For example, there have been observations of flares where the hard X-ray foot point do not form. It is proposed that in these cases the plasma in the coronal loops is so dense that the accelerated particle collide enough to thermalize within the flare loops before reaching the Chromosphere, defusing the energy more evenly within the loop, rather than dumping it at the base of the loops \citep{veronig02,veronig04}. Another flare which previously occurred at the same region might explain the denser coronal loops \citep{strong84,bone07}.

@@

With an experience of observing solar flares for more than 150 years, remarkably enough, we have barely started scratching the surface of the complexity involved with the solar flares. The re-configuring of magnetic structure, which almost always involves complex geometry, making almost all events unique in some sense. After that the released magnetic free energy is transported across various layers of the sun and converted into various other forms of energy. Considering how the energy is transformed the magnetic energy of the active region that is released after the reconnection into the reconnection outflow jets, the kinetic energy of escaping particles, the thermal and the kinetic energy of the Chromospheric plasma evaporating, the radiative and conductive losses. In case of the eruptive events, there is the added complexity of the kinetic and potential energy of the CMEs, the energy of the shocks and the kinetic energy of the solar energetic particles.

In order to constrain the models of solar eruptions and various nuanced aspects of it, like magnetic reconnection, particle acceleration, heating etc. detailed quantitative characterization is absolutely necessary. There have been several studies that have tried to quantify the partition between various subsets of the energies. The questions that are particularly important are:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
    \item \textbf{If an active region can have enough free energy to account for the total energy released in the solar flares and/or CMEs.}
    \item \textbf{What is the energy partition between flares and CMEs.}
    \item \textbf{If the non-thermal component have enough energy to power up the thermal component.}
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

It is generally well known by now that the active region have enough magnetic free energy to power the flare and CME \citep{emslie12,ash17}. The partition of energy between the flare and associated CME is much more fuzzy. \cite{emslie12} found that the flare and CME have energies of same order of magnitude, while \cite{ash17} concluded the flare dominates the CME in-terms of the energy. However the simple question, whether the non-thermal component of the flares have enough energy is still not resolved as even the most recent studies contradict each other in the most puzzling fashion. \cite{warmuth20} discussed the contradictions arising from some of the studies\citep{stosire07,emslie12,inglis14,warmuth16a,warmuth16b,ash17}. The details of the studies can be summarized as follows:

@@

The bolometric energy serves as a representation of the overall energy released during solar flares. Regardless of how energy is released in a solar flare, whether through direct plasma heating, rapid bulk flows, or non thermal particle processes—the ultimate outcome is thermalization and subsequent radiation across the electromagnetic spectrum. Given that bolometric energy encompasses the entire spectrum, it is anticipated to reflect the total energy originally released. It's important to note that this specifically pertains to the energy liberated within the flare and does not encompass the energy associated with a concurrent coronal mass ejection (CME) or filament eruption. \cite{warmuth20} used the bolometric energy released in solar flares, to compare various studies on equal footing. Here we will discuss some of the main issues \cite{warmuth20} identifies comparing these studies.

@@

A possible reason can be attributed to different thermal models used to model the thermal component of the flares. {\it RHESSI} usually yields a higher temperature and lower emission measure compared to {\it GOES} due to the highly multi thermal nature of the flaring plasma \citep{bataglia05,ryan14,warmuth16a}. Although the {\it GOES} temperature is higher by a factor of 1.4, it is not dependant on the flare class. Along with that, \cite{warmuth20} also investigated whether assuming a isothermal or multi thermal model introduces any differences in the thermal energy estimates. They reported no significant differences due to differences of models (refer to Fig. 2 and the corresponding discussion in \cite{warmuth20}).

@@

%%%%%%%%%
\begin{itemize}
    \item The primary challenge in estimating the thermal energy of the hot plasma stems from determining the temperature distribution of the plasma using Differential Emission Measure (DEM), and the radiating plasma volume.
    \item The dissipation of energy from the hot plasma is substantial. Although there is widespread agreement regarding radiative losses across studies, the extent of conductive losses disagree significantly between the studies.
    \item The non-thermal energy in injected electrons is strongly dependent on the poorly constrained low-energy cutoff.
    \item The thermal and non-thermal energy partition changes with flare class. In smaller flares, there appears to be a deficiency of energetic electrons, whereas in larger flares, the injected non-thermal energy seems to sufficient in powering the thermal component. Does this signify the existence of an additional third heating source?
\end{itemize}
%%%%%%%%%

@@

This illustrates the necessity of more observatories operating at the transition region wavelengths for more comprehensive understanding about how the solar flares manifest and affect the dynamics and heating of the lower solar atmosphere. In this regard, {\suit} onboard Aditya-L1 will play a crucial role in probing the lower solar atmosphere. The various imaging channels of {\suit} would observe the manifestation of flares in transition region at various heights (NB3 $\implies$ \ion{Mg}{2} k 279.6 nm, NB4 $\implies$ \ion{Mg}{2} h 280.3 nm, NB8 $\implies$ \ion{Ca}{2} h 396.8 nm), further lower in the transition region (NB2 $\implies$ blue wing of Mg window, NB5 $\implies$ red wing of Mg window) and Sunspots and possible signature of umbral brightening due to flares at the Photosphere (NB6 300 nm and NB7 388 nm) in full disk. This would also allow us to probe the interaction of the flaring region, with other active regions on disk, giving us a comprehensive overview of the effect of solar flares and their manifestation in the lower solar atmosphere.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{itemize}
    \item In chapter \ref{c:chap2}, we review various space based missions available and used in this thesis. We also discuss various analysis techniques used in this thesis. We also motivate the importance of {\suit} and its main science goals. We also briefly discuss the specific questions regarding solar flares we can address with {\suit}.
    \item In chapter \ref{c:chap3}, we discussed some of the initial preparatory analysis we did for {\suit}, including the throughput model for {\suit}, how the filters mounted on {\suit} were chosen, the analysis of spacecraft jitter simulation and what effect it would have on the imaging. We also describe the stellar calibration scheme and the selection criteria for the standard star target. We use a sun as a star spectra to evaluate the calibration scheme with the aforementioned throughput model.
    \item In chapter \ref{c:chap4}, we discuss the forward modelling pipeline developed for {\suit}. We use MPS-Atlas simulation and {\it IRIS} observations, with measured transmission profiles of various optical components and the PSF to forward model {\suit} observations. We also discuss a preliminary version of the deconvolution algorithm that will be deployed in the data reduction pipeline.
    \item In chapter \ref{c:chap5}, we use existing {\it IRIS} observations of three solar flares to probe how the lower solar atmosphere is affected by the flares. The ratio of the \ion{Mg}{2} k and h lines, is a proxy for the optical depth of the surrounding plasma. Hence, we use the observations of \ion{Mg}{2} lines along HMI magnetic field measurements to investigate the effects of magnetic field, if any. \cite{kerr15} conducted a similar study and found signatures of localised heating in the line intensity ratio. We found, that the line intensity ratio shows a correlated increase and decrease with the flare light curve. We argue this to be signature of plasma flow associated with flare, and a change in density of the local environment. This acts as a prelude of what is achievable with {\suit}. We can use a similar method to give full disk context of optical depth, with respect to eruptive events.
    \item We address the issues raised in \S\ref{sol_flr_std_mod} regarding the uncertainties of volume estimation for flaring plasma and its effects on the thermal energy estimation in chapter \ref{c:chap6}. We use observations from {\it SDO}/AIA, {\it STEREO-A}/EUVI, {\it SO}/STIX, {\it GOES}/SUVI to estimate the thermal energy of two solar flares. We propose a new  using existing tools, to use observations from different vantages ({\it e.g.} AIA and EUVI from different angles) to accurately calculate the volume of the flare arcade and estimate the thermal energy. We show that the accurate estimate as a function of time can have effects on the accurate estimation of thermal energy and the partition between the thermal and non-thermal component.
\end{itemize}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
